oREV item selection

### 2022-11-23 analysis/item_selection.Rmd
add clean analysis file

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

@@

@@

easiness_rasch <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>%pull(threshold_mode)
infit <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>% pull(infit_mode)
outfit <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(outfit_mode)
disc_2PL <- coef_irt3$targetWord[, , "logalpha_Intercept"] %>% as_tibble(rownames = "item")%>%pull(Estimate)
```

@@

	spacing <- -1*sd(nn_dists)/10

	row <- tibble(iter = j,
                size = i, 
                mean = spacing)
  easb <- bind_rows(easb,row)
}
}

@@

```{r}
disc_dist <- tibble()

for (i in 1:48) {
x <- sample(disc_2PL, i)
  x_dist <- unlist(lapply(x, func))
  var_x <- -1*var(x_dist)*25
  row <- tibble(iter = j,
                size = i, 
                dist_to_1 = var_x)
  disc_dist <- bind_rows(disc_dist,row)
}
}

ggplot(disc_dist, aes(x = factor(size), y = dist_to_1))+
  geom_point(pch = 1)+
  theme_minimal()

```{r}
infit_dist <- tibble()

for (i in 1:48) {
x <- sample(infit, i)
  x_dist <- unlist(lapply(x, func))
  mean_x <- -4*mean(x_dist)
  row <- tibble(iter = j,
                size = i, 
                dist_to_1 = mean_x)
  infit_dist <- bind_rows(infit_dist,row)
}
}

ggplot(infit_dist, aes(x = factor(size), y = dist_to_1))+
  geom_point(pch = 1)+
  theme_minimal()

```{r}
pkd_dist <- tibble()

for (j in 1:20) {

for (i in 1:48) {
x <- sample(pkd, i)
  mean_x <- mean(x)
  row <- tibble(iter = j,
                size = i, 
                pkd = mean_x)
  pkd_dist <- bind_rows(pkd_dist,row)
}
}

ggplot(pkd_dist, aes(x = factor(size), y = pkd))+
  geom_point(pch = 1)+
  theme_minimal()

```{r}
func <- function(x){
  abs(1-x)
}

outfit_dist <- tibble()

for (i in 1:48) {
  x <- sample(outfit, i)
  x_dist <- unlist(lapply(x, func))
  mean_x <- -1*mean(x_dist)
  row <- tibble(iter = j,
                size = i, 
                dist_to_1 = mean_x)
  outfit_dist <- bind_rows(outfit_dist,row)
}
}

ggplot(outfit_dist, aes(x = factor(size), y = dist_to_1))+
  geom_point(pch = 1)+
  theme_minimal()
```

```{r}
score_fn <- function(subset) {
	easinesses <- sort(easiness[subset])
	nn_dists <- rep(0, sum(subset)-1)
	for(i in 1:sum(subset)-1) {
		nn_dists[i] <- easinesses[i+1] - easinesses[i]
	}
	spacing <- -1*sd(nn_dists)/5

	var_disc_sample <- disc_2PL[subset]
	var_disc_2PL <- -1*var(var_disc_sample)*5

@@

	outfit_sample <- outfit[subset]
	outfit_dist <- unlist(lapply(outfit_sample, func))
  mean_outfit <- -1*mean(outfit_dist)

  mean_pkd <- mean(pkd[subset])/4

@@

  easiness <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>%pull(threshold_mode)
  infit <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>% pull(infit_mode)
  outfit <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(outfit_mode)
  disc_2PL <- coef_irt3$targetWord[, , "logalpha_Intercept"] %>% as_tibble(rownames = "item")%>%pull(Estimate)
  pkd <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(pareto_k)

  #easiness_rasch <- eta_rasch %>% pull(Estimate.eta_Intercept)
  #infit <- rasch_fit_mode %>% filter(fit_index == "infit")%>%pull(mode)
  #infit <- maxi%>%pull(infit)
  #outfit <- rasch_fit_mode %>% filter(fit_index == "outfit")%>%pull(mode)
  #outfit <- maxi%>%pull(outfit)
  #pkd <- maxi%>%arrange(targetWord)%>%pull(influence_pareto_k)
  N <- length(easiness_rasch)

@@

```{r}
sub_rasch <- data%>%
  filter(targetWord %in% sel_items_rasch,
         #!targetWord %in% c("badger", "jaguar","satellite")
         )%>%
  group_by(age_group,subjID)%>%
  summarise(mean_sub = mean(correct))

@@

@@

  for(j in 1:5){

@@

#saveRDS(irt_comp_size, "../saves/irt_comp_size.rds")

#irt_comp_size <- readRDS("../saves/irt_comp_size.rds")

irt_comp_size%>%
  pivot_longer(cols = c(ratio, correlation), names_to = "type",values_to = "value")%>% 
  ggplot(aes(x = factor(size), y = value))+
  geom_point(pch = 1)+
  geom_line()+
  facet_grid(type~. , scales = "free_y")+
  theme_bw()+
  labs(x = "No. of items", y = "Comparison value")
```

@@

   sim <- simulated_annealing(24)

@@

frq_sel_items_rasch <- item_sel_rasch%>%
  group_by(targetWord)%>%
  summarise(n = n()/max(iter))%>%
  arrange(-n)%>%
  slice(1:24)%>%
  pull(targetWord)

@@

```{r}
bind_rows(rasch_fit_sel_guess%>%mutate(fit = "selected items only"),
          rasch_fit%>%mutate(fit = "all items"))%>%
  filter(targetWord %in% rasch_selected_items)%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, fill = fit_index, col = fit_index, lty = fit, pch = fit))+
  geom_vline(xintercept = c(0.5, 1.5), lty = 2, alpha = .5)+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95), position = position_dodge(width = 0.9))+
  scale_fill_colorblind()+
  scale_color_colorblind()+
  labs(title = "Comparing In- and Outfit for 1PL + guessing model with all items vs. selected items",
       x = "Index value", y = "Target word (sorted by rated age of acquisition)")+
  #facet_grid(~fit_index)+
  xlim(0,3)+
  theme_bw()
```
```{r}
ggsave("../graphs/fit_index_comp.png", height = 12, width = 10, scale = 1)
```

>>>>

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

func <- function(x){
  abs(1-x)
}
```

@@

irt1_guess_itemloo <- readRDS("../saves/irt1_guess_itemloo.rds")

@@

items <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>%pull(targetWord)
easiness_rasch <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>%pull(threshold_mode)
infit <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>% pull(infit_mode)
outfit <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(outfit_mode)
disc_2PL <- coef_irt3$targetWord[, , "logalpha_Intercept"] %>% as_tibble(rownames = "item")%>%pull(Estimate)
pkd <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(pareto_k)
```

```{r}
score_dist <- tibble()

for (j in 1:16) {

for (i in 10:35) {

@@

	nn_dists <- rep(0, length(x)-1)

	for(k in 1:length(x)-1) {
		nn_dists[k] <- x[k+1] - x[k]
	}

	x2 <- sample(disc_2PL, i)
  x_dist2 <- unlist(lapply(x2, func))

  x3 <- sample(infit, i)
  x_dist3 <- unlist(lapply(x3, func))

  x4 <- sample(outfit, i)
  x_dist4 <- unlist(lapply(x4, func))

  x <- sample(pkd, i)

  mean_spacing <- -1*sd(nn_dists)/3
  var_2PL <- -1*var(x_dist2)*10
  mean_infit <- -2*mean(x_dist3)
  mean_outfit <- -4*mean(x_dist4)
  mean_pkd <- mean(x)/5

  sum_score = mean_spacing + mean_infit + mean_outfit+ var_2PL +mean_pkd

	row <- tibble(iter = j,
                size = i, 
                spacing = mean_spacing,
	              infit = mean_infit,
	              outfit = mean_outfit,
	              var_2PL_disc = var_2PL, 
	              pkd = mean_pkd, 
	              score = sum_score)

  score_dist <- bind_rows(score_dist,row)
}
}

score_dist%>%
  pivot_longer(cols = c(-size, -iter), names_to = "type", values_to = "value")%>%
  ggplot(aes(x = factor(size), y = value, col = type))+
  geom_point(pch = 1)+
  facet_wrap(~iter)+
  ggtitle("Objectiv")+
  theme_bw()

@@

```{r}
ggsave("../graphs/score.png", height = 12, width = 16, scale = 1)
```

```{r}
score_fn <- function(subset) {
	easinesses <- sort(easiness[subset])
	nn_dists <- rep(0, sum(subset)-1)
	for(i in 1:sum(subset)-1) {
		nn_dists[i] <- easinesses[i+1] - easinesses[i]
	}
	spacing <- -1*sd(nn_dists)/3

	var_disc_sample <- disc_2PL[subset]
	var_disc_2PL <- -1*var(var_disc_sample)*10

@@

	outfit_sample <- outfit[subset]
	outfit_dist <- unlist(lapply(outfit_sample, func))
  mean_outfit <- -2*mean(outfit_dist)

  mean_pkd <- mean(pkd[subset])/5

@@

  items <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>%pull(targetWord)
  easiness <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>%pull(threshold_mode)
  infit <- irt1_guess_itemloo_idxs %>% arrange(targetWord)%>% pull(infit_mode)
  outfit <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(outfit_mode)
  disc_2PL <- coef_irt3$targetWord[, , "logalpha_Intercept"] %>% as_tibble(rownames = "item")%>%pull(Estimate)
  pkd <- irt1_guess_itemloo_idxs%>% arrange(targetWord) %>% pull(pareto_k)

  #easiness_rasch <- eta_rasch %>% pull(Estimate.eta_Intercept)
  #infit <- rasch_fit_mode %>% filter(fit_index == "infit")%>%pull(mode)
  #infit <- maxi%>%pull(infit)
  #outfit <- rasch_fit_mode %>% filter(fit_index == "outfit")%>%pull(mode)
  #outfit <- maxi%>%pull(outfit)
  #pkd <- maxi%>%arrange(targetWord)%>%pull(influence_pareto_k)
  N <- length(easiness)

@@

```{r}
sub_rasch <- data%>%
  filter(targetWord %in% sel_items_rasch,
         #!targetWord %in% c("badger", "jaguar","satellite")
         )%>%
  group_by(age_group,subjID)%>%
  #group_by(subjID)%>%
  summarise(mean_sub = mean(correct))

@@

   sim <- simulated_annealing_rasch(i)

@@

  for(j in 1:3){

  for (i in 10:40) {

    sim <- simulated_annealing_rasch(i)

@@

saveRDS(irt_comp_size, "../saves/irt_comp_size.rds")
saveRDS(irt_comp_size2, "../saves/irt_comp_size2.rds")
# score first round: 
# 	spacing <- -1*sd(nn_dists)/5
# 	var_disc_2PL <- -1*var(var_disc_sample)*5
#   mean_infit <- -4*mean(infit_dist)
#   mean_outfit <- -1*mean(outfit_dist)
#   mean_pkd <- mean(pkd[subset])/4

# score second round: 
# 	spacing <- -1*sd(nn_dists)/3
# 	var_disc_2PL <- -1*var(var_disc_sample)*10
#   mean_infit <- -4*mean(infit_dist)
#   mean_outfit <- -2*mean(outfit_dist)
#   mean_pkd <- mean(pkd[subset])/5

irt_comp_size <- readRDS("../saves/irt_comp_size.rds")

irt_comp_size%>%
  mutate(ratio = ifelse(elpd_diff == 0,0,ratio))%>%
  pivot_longer(cols = c(ratio, correlation), names_to = "type",values_to = "value")%>% 
  ggplot(aes(x = factor(size), y = value))+
  geom_point(pch = 1)+
  geom_line()+
  facet_grid(type~. , scales = "free_y")+
  theme_bw()+
  labs(x = "No. of items", y = "Comparison value")
```

@@

   sim <- simulated_annealing_rasch(20)

@@

frq_sel_items_rasch <- item_sel_rasch%>%
  group_by(targetWord)%>%
  summarise(n = n()/max(iter))%>%
  arrange(-n)%>%
  pull(targetWord)

@@

```{r}
bind_rows(rasch_fit_sel_guess%>%mutate(fit = "selected items only"),
          rasch_fit%>%mutate(fit = "all items"))%>%
  filter(targetWord %in% rasch_selected_items)%>%
  pivot_longer(names_to = "fit_index", values_to = "value", cols = c(outfit, infit))%>%
  ggplot(. , aes(y = fct_reorder(targetWord, aoa_german_comb), x = value, fill = fit_index, col = fit_index, lty = fit, pch = fit))+
  geom_vline(xintercept = c(0.5, 1.5), lty = 2, alpha = .5)+
  geom_vline(xintercept = c(0.7, 1.3), lty = 3, alpha = .5)+
  geom_vline(xintercept = 1, lty = 1, alpha = .5, col = "darkgreen")+
  stat_halfeye(alpha = .75, .width = c(0.66, 0.95), position = position_dodge(width = 0.9))+
  scale_fill_colorblind()+
  scale_color_colorblind()+
  labs(title = "Comparing In- and Outfit for 1PL + guessing model with all items vs. selected items",
       x = "Index value", y = "Target word (sorted by rated age of acquisition)")+
  #facet_grid(~fit_index)+
  xlim(0,3)+
  theme_bw()
```

```{r}
ggsave("../graphs/fit_index_comp.png", height = 12, width = 10, scale = 1)
```
